\hyphenation{ma-te-rials}
%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%
\chapter{Everything}
\label{ch:allandall}

Seesaw mechanism
From Wikipedia, the free encyclopedia

In the theory of grand unification of particle physics, and, in particular, in theories of neutrino masses and neutrino oscillation, the seesaw mechanism is a generic model used to understand the relative sizes of observed neutrino masses, of the order of eV, compared to those of quarks and charged leptons, which are millions of times heavier.

There are several types of models, each extending the Standard Model. The simplest version, “Type 1”, extends the Standard Model by assuming two or more additional right-handed neutrino fields inert under the electroweak interaction,[a] and the existence of a very large mass scale. This allows the mass scale to be identifiable with the postulated scale of grand unification.

neutrinos are left handed

What lepton is displaced:?
why nr has two lines?
What mass ranges are we going to use?
What generator would be used?
What does it mean neutrinos are massless at tree level?
Know someone at ll meeting?

to run code %root -l my_HNL_files/Macros/RHN_Ana.C'("RHN_Mu_13TeV_10k.root")'

\section{arXiv:15041247... Theory paper, Izaguirre}
SM unanswered quetions: Origin of Neutrino masses. the identity of dark matter, and the dynamics responsible for baryon assymetry. A minimal extension of the SM with 3 gauge-singlet 'sterile' right-handed neutrinos (RHN), if they lie below the weak scale, $\nu$MSM.

RHN can be produced by any interaction involving SM neutrinos. i.e $W^{\pm} \to l^{\pm}_\alpha$. Above the bmass, the dominant production mechanism for N is via $W^{\pm} \to l^{\pm}N$ and $Z\to \nu N$

In the standard model of particle physics, the Yukawa couplings encode the interaction between the fundamental fermion fields and the Higgs field, and thus, via the Higgs mechanism, the masses of the fermion field after electroweak symmetry breaking.

DLJ: What is a Displaced LJ?
• LJ: Collimated jet-like structure containing pair(s) of muons
and/or electrons (and/or pions)
• Displaced: Produced far from primary interaction vertex of event

collimated jet-like structures containing pairs of leptons and/or light hadrons, the so-called lepton-jets (LJs).
